\documentclass[margin]{res}
\begin{document}

\name{Angus Findlay}
\address{Glynver, Pines Road, Fleet, Hampshire, GU51 4NL\\
07864 256040\\
(01252) 616190\\
angus.findlay@icloud.com\\
el17ajf@leeds.ac.uk\\
linkedin.com/in/angus-findlay
}

\begin{resume}

\section{Education}
\subsection{The University of Leeds \hfill 2017 - 2021}
Electronics and Computer Engineering MEng.
\subsubsection{Current Modules}
\begin{itemize}
\item Procedural Programming (96\%)
\item Digital Electronics and Microcontrollers (92\%)
\item Computer Architecture (88\%)
\item Communications Networks and Signal (87\%)
\item Engineering Mathematics (86\%)
\item Communications Systems
\item Introduction to Discrete Mathematics
\item Circuit Analysis and Design
\item Programming Project
\item Object Oriented Programming
\end{itemize}
{\sl Grades shown for modules where over half of work has been returned.}
\subsection{The Sixth Form College Farnborough \hfill 2015 - 2017}
Farnborough, Hampshire.
\subsubsection{A Levels}
\begin{itemize}
\item Mathematics A
\item Physics A
\item Computer Science B
\end{itemize}

\newpage

\section{Work Experience}
\subsection{Rushmoor Borough Council \hfill 2017}
Farnborough, Hampshire.\\
Fixed term contract working for the IT department, digitising planning applications and inserting them into the GIS database.
\subsection{Dimension Data \hfill 2016}
Fleet, Hampshire.\\
Work Experience Placement at Dimension Data, a networking and security company.
\subsection{Adsyst Automation \hfill 2014}
Yateley, Hampshire.\\
Work experience placement at Adsyst Automation, a control systems company.

\vspace{1em}

\section{Skills \& Abilities}
\vspace{2em}
Java, C\#, C, C++, SQL, Python, JavaScript.

\vspace{1em}

\section{Leadership Roles}
\subsection{College}
\begin{itemize}
\item Subject Rep and Java Mentor in Computer Science.
\item Form Rep for the student association.
\end{itemize}

\vspace{1em}

\section{References}
\subsection{Dr Andrew H. Kemp}
Form Tutor \& Former Course Manager\\
University of Leeds\\
A.H.Kemp@leeds.ac.uk
\subsection{Dr Craig A. Evans}
Digital Electronics Module Teacher \& Current Course Manager\\
University of Leeds\\
C.A.Evans@leeds.ac.uk

\end{resume}

\end{document}
